Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-07 paper.qmd
Corrected Figure 13 projection

projection <- cbind(
  c(-0.04778, -0.54223, -0.00215, -0.68905),
  c(-0.63659, 0.35753, 0.42558, -0.23854))

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.28,
  axis_pos_x = -0.58,
  axis_pos_y = -0.05,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

five_gau_proj_umap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000",
    linewidth = 1) +
  geom_point(
    #size = 0.5,
    alpha = 0.3,
    color = "#999999") +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 5) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.64, -0.26)) +
  ylim(c(0, -0.38)) +
  interior_annotation("b2", 
                      position = c(0.08, 0.9),
                      cex = 2)

>>>>

projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558, -0.23854, -0.63659, 0.35753))

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.28,
  axis_pos_x = -0.58,
  axis_pos_y = -0.35,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

five_gau_proj_umap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000",
    linewidth = 1) +
  geom_point(
    #size = 0.5,
    alpha = 0.3,
    color = "#999999") +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 5) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.64, -0.29)) +
  ylim(c(-0.4, -0.05)) +
  interior_annotation("b2", 
                      position = c(0.08, 0.9),
                      cex = 2)
